Robust Estimation, Prediction and Control with \\ Continuous States and Dynamics Structure

### 2020-01-13 main.tex
Add ICML template

\documentclass{article}
\usepackage[cm]{fullpage}

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{float}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{caption}
\usepackage{blkarray}
\usepackage{todonotes}
\usepackage{mathtools}
\usepackage[backend=biber,style=authoryear,natbib=true,url=false]{biblatex}

\addbibresource{references.bib}

@@

\title{Robust Estimation, Prediction and Control with Dynamics Structure}
\author{Edouard Leurent, Denis Efimov, Odalric-Ambrym Maillard}
\date{November 2019}

@@

\maketitle

@@

\begin{algorithm}[tp]
  \SetAlgoLined\DontPrintSemicolon
  \SetKwFunction{algo}{robust\_control}
  \SetKwFunction{proc}{pessimistic\_step}
  \SetKwProg{myalg}{Algorithm}{}{}
  \myalg{\algo{$s_0$}}{
  \While{resources available}
  {
  Select a candidate action sequence $a$ with a planning algorithm.\;
  Sample a pessimistic transition and reward $\underline{r}_t$ using \proc{$\underline{x}(t)$, $\overline{x}(t)$, a}.
 \;
 Update the planning algorithm with the sampled pessimistic transition.
  }
  \KwRet $\argmax_{\pi\in\Pi} \hat{v^r}(\pi)$ \;}{}
  \setcounter{AlgoLine}{0}
  \SetKwProg{myproc}{Procedure}{}{}
  \myproc{\proc{$\underline{x}(t)$, $\overline{x}(t)$, $a$}}{
  Integrate \eqref{eq:interval_predictor} over $dt$ with controls $a$ to compute $\underline{x}(t+dt), \overline{x}(t+dt)$\;
  Compute worst-case reward $\underline{r}_t = \min_{x\in[\underline{x}(t), \overline{x}(t)]} r(x)$\;
  \KwRet $\underline{x}(t+dt), \overline{x}(t+dt), \underline{r}_t$\;}
\caption{Interval-based Robust Control}
\label{algo:irc}

\end{algorithm}

@@

\begin{algorithm}[tp]
\DontPrintSemicolon
Initialize $\mathcal{T}$ to a root and expand it. Set $n=1$.\;
\While{Numerical resource available for episode $n$}{
Compute the robust b-values $b^r_i(n)$.\;
Expand the leaf $\argmax_{i\in \mathcal{L}_n} b^r_i(n)$.\;
}
\Return $\argmax_{a\in \mathcal{A}} u^r_a(n)$
\caption{Deterministic Robust Optimistic Planning}
\label{algo:drop}
\end{algorithm}

@@

\printbibliography

>>>>

%%%%%%%% ICML 2020 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%

\documentclass{article}

% Recommended, but optional, packages for figures and better typesetting:
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{booktabs} % for professional tables

% hyperref makes hyperlinks in the resulting PDF.
% If your build breaks (sometimes temporarily if a hyperlink spans a page)
% please comment out the following usepackage line and replace
% \usepackage{icml2020} with \usepackage[nohyperref]{icml2020} above.
\usepackage{hyperref}

% Attempt to make hyperref and algorithmic work together better:
\newcommand{\theHalgorithm}{\arabic{algorithm}}

% Use the following line for the initial blind version submitted for review:
\usepackage{icml2020}

% If accepted, instead use the following line for the camera-ready submission:
%\usepackage[accepted]{icml2020}

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
%\icmltitlerunning{Submission and Formatting Instructions for ICML 2020}

% Custom packages
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{float}
\usepackage{hyperref}
\usepackage{blkarray}
\usepackage{todonotes}
\usepackage{mathtools}

@@

%\author{Edouard Leurent, Denis Efimov, Odalric-Ambrym Maillard}

@@

	\twocolumn[
	\icmltitle{Robust Estimation, Prediction and Control with \\ Continuous States and Dynamics Structure}

	% It is OKAY to include author information, even for blind
	% submissions: the style file will automatically remove it for you
	% unless you've provided the [accepted] option to the icml2020
	% package.

	% List of affiliations: The first argument should be a (short)
	% identifier you will use later to specify author affiliations
	% Academic affiliations should list Department, University, City, Region, Country
	% Industry affiliations should list Company, City, Region, Country

	% You can specify symbols, otherwise they are numbered in order.
	% Ideally, you should not use this facility. Affiliations will be numbered
	% in order of appearance and this is the preferred way.
	\icmlsetsymbol{equal}{*}

	\begin{icmlauthorlist}
		\icmlauthor{Edouard Leurent}{seq,val,ren}
		\icmlauthor{Denis Efimov}{val}
		\icmlauthor{Odalric Ambrym-Maillard}{seq}
	\end{icmlauthorlist}

	\icmlaffiliation{seq}{Inria Lille Nord-Europe, Sequel Project, Lille, France}
	\icmlaffiliation{val}{Inria Lille Nord-Europe, Valse Project, Lille, France}
	\icmlaffiliation{ren}{Renault Group, Guyancourt, France}

	\icmlcorrespondingauthor{Edouard Leurent}{edouard.leurent@inria.fr}

	% You may provide any keywords that you
	% find helpful for describing your paper; these are used to populate
	% the "keywords" metadata in the PDF but will not be shown in the document
	\icmlkeywords{Machine Learning, ICML}

	\vskip 0.3in
	]

	% this must go after the closing bracket ] following \twocolumn[ ...

	% This command actually creates the footnote in the first column
	% listing the affiliations and the copyright notice.
	% The command takes one argument, which is text to display at the start of the footnote.
	% The \icmlEqualContribution command is standard text for equal contribution.
	% Remove it (just {}) if you do not need this facility.

	\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
%	\printAffiliationsAndNotice{\icmlEqualContribution} % otherwise use the standard text.

	\begin{abstract}
		This document provides a basic paper template and submission guidelines.
		Abstracts must be a single paragraph, ideally between 4--6 sentences long.
		Gross violations will trigger corrections at the camera-ready phase.
	\end{abstract}

\section{Introduction}

@@

%\begin{algorithm}[tp]
%  \SetAlgoLined\DontPrintSemicolon
%  \SetKwFunction{algo}{robust\_control}
%  \SetKwFunction{proc}{pessimistic\_step}
%  \SetKwProg{myalg}{Algorithm}{}{}
%  \myalg{\algo{$s_0$}}{
%  \While{resources available}
%  {
%  Select a candidate action sequence $a$ with a planning algorithm.\;
%  Sample a pessimistic transition and reward $\underline{r}_t$ using \proc{$\underline{x}(t)$, $\overline{x}(t)$, a}.
% \;
% Update the planning algorithm with the sampled pessimistic transition.
%  }
%  \KwRet $\argmax_{\pi\in\Pi} \hat{v^r}(\pi)$ \;}{}
%  \setcounter{AlgoLine}{0}
%  \SetKwProg{myproc}{Procedure}{}{}
%  \myproc{\proc{$\underline{x}(t)$, $\overline{x}(t)$, $a$}}{
%  Integrate \eqref{eq:interval_predictor} over $dt$ with controls $a$ to compute $\underline{x}(t+dt), \overline{x}(t+dt)$\;
%  Compute worst-case reward $\underline{r}_t = \min_{x\in[\underline{x}(t), \overline{x}(t)]} r(x)$\;
%  \KwRet $\underline{x}(t+dt), \overline{x}(t+dt), \underline{r}_t$\;}
%\caption{Interval-based Robust Control}
%\label{algo:irc}
%
%\end{algorithm}

@@

%\begin{algorithm}[tp]
%\DontPrintSemicolon
%Initialize $\mathcal{T}$ to a root and expand it. Set $n=1$.\;
%\While{Numerical resource available for episode $n$}{
%Compute the robust b-values $b^r_i(n)$.\;
%Expand the leaf $\argmax_{i\in \mathcal{L}_n} b^r_i(n)$.\;
%}
%\Return $\argmax_{a\in \mathcal{A}} u^r_a(n)$
%\caption{Deterministic Robust Optimistic Planning}
%\label{algo:drop}
%\end{algorithm}

@@

\bibliography{references}
\bibliographystyle{icml2020}
